---
title: "Prediction_Project"
author: "David Zepeda"
date: "8/3/2022"
output:
  pdf_document: default
  html_document: default
---


```{r setup, include = FALSE}
# DO NOT ALTER THIS CHUNK
knitr::opts_chunk$set(
  echo = TRUE,
  eval = TRUE,
  fig.width = 5,
  fig.asp = 0.618,
  out.width = "70%",
  dpi = 120,
  fig.align = "center",
  cache = FALSE
)
# Cost function for cross validation
cost <- function(obs, pred) {
  outcome <- pred > 0.5
  return(1 - (sum(obs == outcome) / length(obs)))
}
# Load required packages
library(tidyverse)
library(ggmosaic)
library(modelr)
library(boot)
library(broom)
install.packages("rpart.plot")
library(rpart.plot)
library(ggplot2)

```


#Opening of the CSV and naming under prediction_data

```{r}
  prediction_data <- read.csv(file = "Capstone_project_data_csv.csv")

```

#Displaying the Top of the dataset

```{r}
  head(prediction_data)

```


#Summary statistics of data from beginning 

```{r}
  summary(prediction_data)
```

#Bar Graph of county and homes acquired from there


```{r}
prediction_data%>%
      ggplot() +
      geom_bar(mapping = aes(x = County, fill = County)) + theme(axis.text.x = element_text(angle = 50))
      labs(title = "County distribution" ,
           x = "County")
```

#Histogram of the incomes 

```{r}
  prediction_data %>%
      ggplot() +
      geom_histogram(mapping = aes(x = Income_average))+
      labs(title = "Income Distribution", 
           x = "Total Income")

```

#Summary of just the Home_Price

```{r}
  prediction_data%>%
summarise(
mean = mean(Home_Price),
median = median(Home_Price),
sd = sd(Home_Price),
iqr = IQR(Home_Price),
min = min(Home_Price),
max = max(Home_Price)
)




```

#Boxplot of Income_average of the first dataset

```{r}
      boxplot(prediction_data$Income_average)
```



#lm model of home price over average home price


```{r}
  model.lm <- lm(formula = Home_Price ~ Price_Home_average , data = prediction_data)
summary(model.lm)
```

#Filtering per county In this case montgomery 

```{r}
  Mont_data <- prediction_data %>% 
  filter(ID <= 5)
```



```{r}
  Mont_data %>%
      ggplot() +
      geom_line(mapping = aes(x = Address, y = Home_Price, group = 1), color = 'red') + theme(axis.text.x = element_text(angle = 50))+
      labs(title = "Current Home Prices in Montgomery", 
           x = "Address")

```



#Filtering per county In this case Loudoun



```{r}
  Loud_data <- prediction_data %>% 
  filter(ID >= 6 & ID <= 10)
```

```{r}
 Loud_data %>%
      ggplot() +
      geom_line(mapping = aes(x = Address, y = Home_Price, group = 1), color = 'blue') + theme(axis.text.x = element_text(angle = 50))+
      labs(title = "Current Home Prices in Loudoun", 
           x = "Address")

```

#Filtering per county In this case Cecil

```{r}
  Cecil_data <- prediction_data %>% 
  filter(ID >= 11 & ID <= 15)
```


```{r}
 Cecil_data %>%
      ggplot() +
      geom_line(mapping = aes(x = Address, y = Home_Price, group = 1), color = 'green') + theme(axis.text.x = element_text(angle = 50))+
      labs(title = "Current Home Prices in Cecil", 
           x = "Address")

```


#Filtering per county In this case Howard


```{r}
  How_data <- prediction_data %>% 
  filter(ID >= 16 & ID <= 20)
```

```{r}
 How_data %>%
      ggplot() +
      geom_line(mapping = aes(x = Address, y = Home_Price, group = 1), color = 'purple') + theme(axis.text.x = element_text(angle = 30))+
      labs(title = "Current Home Prices in Howard", 
           x = "Address")

```

#Filtering per county In this case Frederick


```{r}
  Fred_data <- prediction_data %>% 
  filter(ID >= 21 & ID <= 27)
```


```{r}
 Fred_data %>%
      ggplot() +
      geom_line(mapping = aes(x = Address, y = Home_Price, group = 1), color = 'orange') + theme(axis.text.x = element_text(angle = 50))+
      labs(title = "Current Home Prices in Frederick", 
           x = "Address")

```

#Filtering per county In this case Prince George


```{r}
  PRF_data <- prediction_data %>% 
  filter(ID >= 28 & ID <= 35)
```


```{r}
 PRF_data %>%
      ggplot() +
      geom_line(mapping = aes(x = Address, y = Home_Price, group = 1), color = 'brown') + theme(axis.text.x = element_text(angle = 50))+
      labs(title = "Current Home Prices in Prince George", 
           x = "Address")

```

#Filtering per county In this case Charles


```{r}
  Char_data <- prediction_data %>% 
  filter(ID >= 36 & ID <= 40)
```

```{r}
 Char_data %>%
      ggplot() +
      geom_line(mapping = aes(x = Address, y = Home_Price, group = 1), color = 'black') + theme(axis.text.x = element_text(angle = 35))+
      labs(title = "Current Home Prices in Charles", 
           x = "Address")

```

#Filtering per county In this case Fairfax


```{r}
  Fair_data <- prediction_data %>% 
  filter(ID >= 41 & ID <= 45)
```


```{r}
 Fair_data %>%
      ggplot() +
      geom_line(mapping = aes(x = Address, y = Home_Price, group = 1), color = 'red') + theme(axis.text.x = element_text(angle = 25))+
      labs(title = "Current Home Prices in Fairfax", 
           x = "Address")

```

#Separate summaries by counties

```{r}
  summary(Mont_data)
```


```{r}
  summary(Loud_data)
```

```{r}
  summary(Cecil_data)
```




```{r}
  summary(How_data)
```


```{r}
  summary(Fred_data)
```



```{r}
  summary(PRF_data)
```



```{r}
  summary(Char_data)
```

```{r}
  model_1 <- lm(Income_average ~ Home_Price, data = prediction_data, y = TRUE, x = TRUE)

```


```{r}
  model_1 %>%
tidy()

```

```{r}
  model_1 %>%
glance()

```


```{r}
      model_pre2 <- glm(
        Home_Price ~ Income_average + Price_Home_average ,
        data = prediction_data
      )
```

```{r}
      summary(model_pre2)
```


```{r}
      preds1 <- predict(model_pre2, type = "response")
```



#loading each county with an 6% inflation rate

```{r}
    New_mont <- Mont_data
  

```


```{r}
New_mont <- Mont_data%>%
 
 mutate(
   Inf_rate =  Income_average * .066,
  Income_average = Income_average + Inf_rate
 )

```



```{r}
      model_pre3 <- glm(
        Home_Price ~ Income_average + Price_Home_average+ Inf_rate ,
        data = prediction_data
      )
```


```{r}
      preds2 <- predict(model_pre2, type = "response")
```

```{r}
      summary(model_pre3)
```


```{r}
    New_Loud <- Loud_data
  

```


```{r}
New_Loud <- Loud_data%>%
 
 mutate(
   Inf_rate =  Income_average * .066,
  Income_average = Income_average + Inf_rate
 )

```


```{r}
    New_Cecil <- Cecil_data
  

```


```{r}
New_Cecil <- Cecil_data%>%
 
 mutate(
   Inf_rate =  Income_average * .066,
  Income_average = Income_average + Inf_rate
 )

```


```{r}
    New_How <- How_data
  

```


```{r}
New_How <- How_data%>%
 
 mutate(
   Inf_rate =  Income_average * .066,
  Income_average = Income_average + Inf_rate
 )

```

```{r}
    New_Fred <- Fred_data
  

```


```{r}
New_Fred <- Fred_data%>%
 
 mutate(
   Inf_rate =  Income_average * .066,
  Income_average = Income_average + Inf_rate
 )

```

```{r}
    New_PRF <- PRF_data
  

```


```{r}
New_PRF <- PRF_data%>%
 
 mutate(
   Inf_rate =  Income_average * .066,
  Income_average = Income_average + Inf_rate
 )

```


```{r}
    New_Char <- Char_data
  

```


```{r}
New_Char <- Char_data%>%
 
 mutate(
   Inf_rate =  Income_average * .066,
  Income_average = Income_average + Inf_rate
 )

```

```{r}
    New_Fair <- Fair_data
  

```


```{r}
New_Fair <- Fair_data%>%
 
 mutate(
   Inf_rate =  Income_average * .066,
  Income_average = Income_average + Inf_rate
 )

```


#small tree model that displays the income per county

```{r}
model.tree1 <- rpart(Income_average ~., data = prediction_data, method = 'anova')
summary(model.tree1)
rpart.plot(model.tree1)
plotcp(model.tree1)
```


#Binding all separated county set into one


```{r}
  
  new_predictedset <- rbind( New_mont, New_Loud, New_How,
        New_Fred, New_PRF, New_Char, New_Fair,New_Cecil)

```

```{r}
  arrange(new_predictedset, ID, .by_group = FALSE)

```


```{r}

  pre_df<- new_predictedset %>%
add_predictions(model_pre3) %>%
add_residuals(model_pre3)

```

#point model of the new incomes with the inflation rate intop

```{r}
  pre_df %>%
ggplot() +
geom_point(mapping = aes(x = Home_Price, y = pred)) +
geom_abline(slope = 1, intercept = 0) +
labs(title=" Price of Homes ")




```


```{r}
  K_pred_df <- pre_df%>%
  select(Income_average, Price_Home_average, Home_Price,Inf_rate, pred, resid)


```





```{r}
pred_cluster <-kmeans(K_pred_df, 2)


```

```{r}
  kmean_pred <- function(k) {
    cluster <- kmeans(K_pred_df, 2)
    return (cluster$kmean_pred)
}


```

```{r}
kmean_pred(2)


```

```{r}

k_max <-10
range_k <- sapply(10:k_max, kmean_pred)


```


```{r}

  k_elbow <-data_frame(2:k_max, range_k)

```


#The new income distribution whihc is higher than the older model

```{r}
  new_predictedset %>%
      ggplot() +
      geom_histogram(mapping = aes(x = Income_average))+
      labs(title = "New Income Distribution", 
           x = "New Needed Income")

```

#Boxplot of new income average after inflation

```{r}
      boxplot(new_predictedset$Income_average)
```

#summary of new statistics

```{r}
  summary(new_predictedset)
```


```{r}
  pre_df %>%
ggplot() +
geom_point(mapping = aes(x = Income_average, y = County)) +
geom_abline(slope = 1, intercept = 0) +
labs(title=" New Income")




```




Old average Income 

```{r}
  prediction_data %>%
ggplot() +
geom_point(mapping = aes(x = Income_average, y = County)) +
geom_abline(slope = 1, intercept = 0) +
labs(title=" old Income")




```

#comparision of old and new incomes needed

```{r}
 pre_df %>%
      ggplot() +
      geom_line(mapping = aes(x = County, y = Income_average, group = 1), color = 'red') + theme(axis.text.x = element_text(angle = 25))+
      labs(title = "New Income Average", 
           x = "County")

```



```{r}
 prediction_data %>%
      ggplot() +
      geom_line(mapping = aes(x = County, y = Income_average, group = 1), color = 'red') + theme(axis.text.x = element_text(angle = 25))+
      labs(title = "Old Income Average", 
           x = "County")

```



```{r}
 pre_df %>%
      ggplot() +
      geom_line(mapping = aes(x = County, y = Inf_rate, group = 1), color = 'red') + theme(axis.text.x = element_text(angle = 25))+
      labs(title = "Current Home Prices in Fairfax", 
           x = "Address")

```

```{r}
  pre_df%>%
  summary(Inf_rate)

```


```{r}
  plot(model_pre3)

```


```{r}
      model_pre4 <- glm(
        Income_average ~ Home_Price,
        data = pre_df
      )
```


```{r}
  plot(model_pre4)

```


```{r}
      summary(model_pre4)
```

```{r}
      model_pre5 <- glm(
        Home_Price ~ Income_average + Price_Home_average+ Inf_rate ,
        data = K_pred_df
      )
```


```{r}
      summary(model_pre5)
```


```{r}
model.tree1 <- rpart(Income_average ~ Home_Price, data = K_pred_df, method = 'anova')
summary(model.tree1)
rpart.plot(model.tree1)
plotcp(model.tree1)
```










